Automating Verification of MPC Security

### 2023-06-06 popl24/minicat.tex
checkpoint

The $\minifed$ language provides a simple model of synchronous
protocols between a federation of \emph{clients} exchanging values in
the binary field. We will identify clients by natural numbers, and
federations- finite sets of clients- are always given statically.
As we will see, our threat model assumes a partition of the federation
into \emph{honest} and \emph{corrupt} subsets.

@@

Expressions also include $\select{\be_1}{\be_2}{\be_3}$ which is
like a conditional expression in the binary field with:
$$
\select{\be_1}{\be_2}{\be_3} \equiv (\be_1\ \eand\ \be_2)\ \eor\ (\enot\ \be_1\ \eand\ \be_3)
$$
We also include \emph{oblivious transfer} $\OT{\be_1}{\be_2}{\be_3}$ as a primitive,
with semantics similar to $\ttt{select}$ but with important nuances
related to communication between clients as we discuss more below.
As we will demonstrate, it is not necessary to include $\ttt{OT}$
as a primitive since we can implement it in a provably secure
fashion. However its inclusion simplifies our presentation and is a useful
convenience.

@@

\begin{definition}[Memories]
A \emph{memory}, aka \emph{store} $\store$ is a finite (partial) mapping from variables to values.
The \emph{domain} of a memory is written $\dom(\store)$ and is the finite
set of variables on which the memory is defined. We write $\store\{ x \mapsto v\}$
for  $x\not\in\dom(\store)$ to denote the memory $\store'$ such that $\store'(x) = v$ and otherwise
$\store'(y) = \store(y)$ for all $y \in \dom(\store)$.
\end{definition}

@@

\paragraph{Variable and Memory Conventions} Given a program $\prog$, we
write $\iov(\prog)$ to denote the pair $(S,V)$
where $S$ is the set of secret variables in $\prog$ and
$V$ is the set of views in $\prog$, and we write $\flips(\prog)$ to
denote the set $F$ of flip variables in $\prog$. For any set of variables $X$
and parties $P$, we write $X_P$ to denote the subset
of $X$ owned by any party in $P$, and we write $X_H$ and
$X_C$ to denote the subsets belonging to honest and
corrupt parties, respectively.

Given a set of variables $X$, we write $\store_X$ to mean the memory
$\store$ restricted to the domain $X$, and
and we define $\mems(X)$ as:
$$
\mems(X) \defeq \{ \store \mid \dom(\store) = X \}
$$
We will also write $\store_1 \cup \store_2$ to denote
the memory resulting by combining disjoint
memories $\store_1$ and $\store_2$, i.e.,
under the assumption that $\dom(\store_1) \cap \dom(\store_2) = \varnothing$.

>>>>

The $\minifed$ language provides a simple model of synchronous
protocols between a federation of \emph{clients} exchanging values in
the binary field. We will identify clients by natural numbers, and
federations- finite sets of clients- are always given statically.
As we will see, our threat model assumes a partition of the federation
into \emph{honest} $H$ and \emph{corrupt} $C$ subsets.

@@

We let $X$ range over sets of variables and $S,V,F$ to range over sets
of secrets, views, and flips respectively. Given a program $\prog$, we
write $\iov(\prog)$ to denote the pair $(S,V)$ where $S$ is the set of
secret variables in $\prog$ and $V$ is the set of views in $\prog$,
and we write $\flips(\prog)$ to denote the set $F$ of flip variables
in $\prog$. For any set of variables $X$ and parties $P$, we write
$X_P$ to denote the subset of $X$ owned by any party in $P$, and we
write $X_H$ and $X_C$ to denote the subsets belonging to honest and
corrupt parties, respectively.

Expressions forms include the convenience
$\select{\be_1}{\be_2}{\be_3}$ which is like a conditional expression
in the binary field with:
$$
\select{\be_1}{\be_2}{\be_3} \equiv (\be_1\ \eand\ \be_2)\ \eor\ (\enot\ \be_1\ \eand\ \be_3)
$$
We also include \emph{oblivious transfer} $\OT{\be_1}{\be_2}{\be_3}$ as a primitive,
with semantics similar to $\ttt{select}$ but with important nuances
related to communication between clients as we discuss more below.
As we will demonstrate, it is not necessary to include $\ttt{OT}$
as a primitive since we can implement it in a provably secure
fashion. However its inclusion simplifies our presentation and is a useful
convenience.

@@

\emph{Memories} are fundamental to the semantics of $\fedcat$ and
provide the random tape and secret inputs to protocols, and record
view assignments. Memories $\store$ are finite (partial) mapping from
variables to values. The \emph{domain} of a memory is written
$\dom(\store)$ and is the finite set of variables on which the memory
is defined. We write $\store\{ x \mapsto v\}$ for
$x\not\in\dom(\store)$ to denote the memory $\store'$ such that
$\store'(x) = v$ and otherwise $\store'(y) = \store(y)$ for all $y \in
\dom(\store)$.

Given a set of variables $X$, we write $\store_X$ to denoted the
memory $\store$ restricted to the domain $X$, and and we define
$\mems(X)$ as the set of all memories with domain $X$:
$$
\mems(X) \defeq \{ \store \mid \dom(\store) = X \}
$$
Thus, given a protocol $\prog$, the set of all random tapes for
$\prog$ is $\mems(\flips(\prog))$. We let $\stores$ range
over sets of memories.

Given a variable-free boolean expression $\be$, we write
$\cod{\be}$ to denote the standard interpretation of $\be$.
With the introduction of variables to expressions, we
have two concerns. First, we need to interpret expressions
with respect to a specific memory, and second, we need
to ensure that variables are used ``legally''. That is,
since expressions define local computation, all variables
used in an expression must belong to the same client.

@@
